Figures

### 2018-11-05 figures/01_county_extent.Rmd
pull 2010 cdl not 2008

ep <- readRDS("data/ep.rds")
gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
# st_layers(gdb_path)
layer_name <- "COUNTY"
county <- st_read(gdb_path, layer_name, quiet = TRUE)
states <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))

@@

lg          <- lagosne_load("1.087.1")
iws_lulc    <- readRDS("data/iws_lulc.rds")
county_lulc <- readRDS("data/county_lulc.rds")

>>>>

ep <- readRDS("../data/ep.rds")
gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
# st_layers(gdb_path)
layer_name <- "COUNTY"
county <- st_read(gdb_path, layer_name, quiet = TRUE)
states <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))

@@

lg          <- lagosne_load("1.087.1")
iws_lulc    <- readRDS("../data/iws_lulc.rds")
county_lulc <- readRDS("../data/county_lulc.rds")

### 2018-11-05 manuscript/figures.Rmd
cleanup animal plots
pull 2010 cdl not 2008

```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 1995 and 2005.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/01_county_extent-1.pdf")
```

@@

>>>>

```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/01_county_extent-1.pdf")
```

@@

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```
